------------------------------------------------------------------------
MDATOMS:
------------------------------------------------------------------------
MDCLATOMS_INFO : information about the atoms : charges, masses ...
MDATOM_MAPS    : more detailed information about the atoms : 
what molecule is it in, what residue, what is
an atoms type ...
MDCLATOMS_TRAN : part of the path integral methodology.
------------------------------------------------------------------------


------------------------------------------------------------------------
MDINTER :
------------------------------------------------------------------------
MDENERGY_CTRL  : control multiple time step integration,
               type of ewald summation, ...
               MDPART_MESH    : 
MDINTERACT     : information about the intermolecular potential
MDNBR_LIST     : Verlet neighbor list controls
MDBRNCH_ROOT :
MDLNKLIST    :
MDVERLIST    :
MDSURFACE      : Surface potentials
------------------------------------------------------------------------


------------------------------------------------------------------------
GEN :
------------------------------------------------------------------------
GENSTATEPOINT  : temperature, pressure, surface tension of system
GENCELL        : periodicity, volume of system
GENTIMEINFO    : number of time steps, present time step, time step size,
               multiple time step integration options.
               GENBARO        : class for isotropic constant pressure integration
               GENPAR_RAHMAN  : class for flexible constant pressure integration
                                      GENPTENS       : instantaneous pressure of simulation
                                                       GENSTAT_AVG    : statistical averages accumulated during the run.
                                                       GENEWALD       : information used to compute the Ewald sums
                                                       GENSIMOPTS     : type of run : md, minimization, ...
                                                       GENMINOPTS     : type of minimization : conjugate gradient, diis
                                                       GENENSOPTS     : type of ensemble, constant volume and energy,
                                                       constant volume and temperature, ...
                                                       GENFILENAMES   : input/output file names
                                                       ------------------------------------------------------------------------


                                                       ------------------------------------------------------------------------
                                                       MDINTEGRATE :
                                                       ------------------------------------------------------------------------
                                                       MDTHERM_INFO   : information for constant temperature integration.
                                                       MDVEL_SAMP     : information about velocity refreshing
                                                       ------------------------------------------------------------------------


                                                       ------------------------------------------------------------------------
                                                       MDINTRA :
                                                       ------------------------------------------------------------------------
                                                       MDBOND           : bonds in simulation
                                                       MDBEND           : bends in simulation
                                                       MDBEND_BND       : uri-bradleys in simulation
                                                       MDTORS           : torsions in simulation
                                                       MDONFO           : one-four interactions in simulation
                                                       MDECOR           : corrections to the reciprocal space part of the 
                                                       Ewald sum.
                                                       MDEXCL           : exclusion list.
                                                       MDGRP_BOND_CON   : rigid groups, lines, triangles ...
                                                       MDCONSTRNT       : control for the constraints.
                                                       MDGRP_BOND_WATTS : fancy flexible bonds
                                                       MDGHOST_ATOMS    : fixed point sources in simulation
                                                       MDBOND_FREE      : bond free energy profile structure
                                                       MDBEND_FREE      : bend free energy profile structure
                                                       MDTORS_FREE      : tors free energy profile structure
                                                       MDRBAR_SIG_FREE  : mean-std free energy profile structure
                                                       ------------------------------------------------------------------------


                                                       ------------------------------------------------------------------------
                                                       CP :
                                                       ------------------------------------------------------------------------
                                                       CPOPTS        : Basic options for the method :
                                                       exc-type,lda/lsda,orthog-type,binary read/write,
                                                       coef temperature, minimization tolerence, hessian on/off,
                                                       pressure tensor on/off
                                                       CPCOEFFS_INFO : Information describing the electronic states :
                                                       number of state, number of coefs, plane wave cutoff,
                                                       masses, occupation numbers.
                                                       CPTHERM_INFO  : Thermostatting of e-states for CP dynamics :
                                                       number and types of thermstats, thermostat parameters,
                                                       map of thermstat to coefs.
                                                       CPATOM_MAPS   : Description of atoms for CP :
                                                       number and identity of ab initio atoms,
                                                       number and identity of ab initio atoms with non-local
                                                       pseudopotential.
                                                       CPCONSTRNT    : Constraint tolerence for CP dynamics.
                                                       CPEWALD       : Allowed g-vectors on the large and small reciprocal space.
                                                       CPPSEUDO      : Spline lookup of local and non-local pseudopotentials.
                                                       CPDUAL_PME    : QM/MM : needs to do some PME for e-density.
                                                       CPATOM_PME    : QM/MM : needs to do some PME for the atoms.
                                                       CPVEL_SAMP    : Choose new velocities for the plane-wave coefs.
                                                       CPYLM_CONS    : Constants to help with non-local pseudopotentials.
                                                       ------------------------------------------------------------------------
